Stat 400 Project

### 2021-12-05 Stat 400 proj.Rmd
Fixed simulation error, turns out it didnt make sense to see which sus ppl get infected when theres no sus ppl

  current_non_infected <- rbind(current_suceptable, current_removed)

  #store new infection status
  new_status <- rep(NA, nrow(current_non_infected))
  newly_infected <- NULL

  #Check to see which susceptible subjects get infected
  #For loop

  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_non_infected)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_non_infected[j, 'x'])
      y_s <- as.numeric(current_non_infected[j, 'y'])

      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      print(c(d <= crucial_distance, x_i, x_s))
      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }

    }
  }
  current_non_infected[newly_infected, 3] <- 'I'
  #Give incubation time
  current_non_infected[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
  #Give recovery time
  current_non_infected[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)

  new_state <- rbind(current_infected, current_non_infected)
  return(new_state)
}

@@

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      print(checked_positions)
      new_status <- infection_status(checked_positions, 2)

      not_recovered = new_status[new_status[, 5] > 0]
      new_time <- not_recovered[, 5] - 1
      not_recovered[, 5] <- new_time
      infected_0 <- new_status[new_status[, 5] == 0]
      infected_0[, 3] <- 'R'
      not_infected = new_status[new_status[, 5] < 0]

@@

      not_recovered = new_status[new_status[, 5] > 0]
      new_time <- not_recovered[, 5] - 1
      not_recovered[, 5] <- new_time
      infected_0 <- new_status[new_status[, 5] == 0]
      infected_0[, 3] <- 'R'
      not_infected = new_status[new_status[, 5] < 0]

@@

    }
  }
  return(end_day[[3]])
}

#Testing
df <- starting_vals(100, 2, 10, 10)
len <- get_step_length(df, 10, 10)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 10, 10)
new_status <- infection_status(coords, 2)
new_status

>>>>

  #store new infection status
  newly_infected <- NULL

  #Check to see which susceptible subjects get infected
  #For loop
  if(nrow(current_suceptable) != 0){
  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_suceptable)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])

      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      # print(c(d <= crucial_distance, x_i, x_s, j, i, nrow(current_infected)))
      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }

    }
  }

  current_suceptable[newly_infected, 3] <- 'I'
  #Give incubation time
  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
  #Give recovery time
  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)

  new_state <- rbind(current_infected, current_suceptable, current_removed)
  return(new_state)
  }else{return(state)}
}

@@

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 2)

      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
      new_time <- as.numeric(not_recovered[, 5]) - 1
      not_recovered[, 5] <- new_time
      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
      infected_0[, 3] <- rep('R', nrow(infected_0))
      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]

@@

      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
      new_time <- as.numeric(not_recovered[, 5]) - 1
      not_recovered[, 5] <- new_time
      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
      infected_0[, 3] <- rep('R', nrow(infected_0))
      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]

@@

    }
  }
  return(end_day[[1]])
}

#Testing
df <- starting_vals(10, 2, 1, 1)
len <- get_step_length(df, 1, 1)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 1, 1)
coords
new_status <- infection_status(coords, 2)
new_status
